\MakeUppercase{Graph Product Structure for Non-Minor-Closed Classes}

### 2022-11-03 k-planar.tex
Import typo fix, x -> x'
Typo fix

  Suppose, without loss of generality, that $v_0$ participates in $x_i$.  Then $a(v_0)=x$ is a $T$-ancestor of $x_i$ which a $T$-ancestor of $x_r$.  Finally $a(v_r)=y$ is a $T$-ancestor of $x_r$.  Therefore, both $x$ and $y$ are contained in the path from the root of $T$ to $x_r$, so at least one of $x$ or $y$ is a $T$-ancestor of the other.  This completes the proof of \cref{i-ancestor}
\end{proof}

@@

\begin{proof}
  For the tree-decomposition $(C_x:x\in V(T))$ of $J$ we use the same tree $T$ used in the tree-decomposition $(B_x:x\in V(T))$ of $H$. For each node $x$ of $T$, we define $C_x$ as follows: $C_x$ contains $x$ as well as every $T$-ancestor $a$ of $x$ such that $J$ contains an edge $ax'$ where $x$ is a $T$-ancestor of $x'$ (including the possibility that $x=x'$).
  \cref{i-ancestor} ensures that, for every edge $ax'\in E(J)$, both $a$ and $x$ are contained in $C_{x'}$\todo{Do we mean $C_x$ here?}.  The connectivity of $T[a]:=T[\{x\in V(T):a\in C_x\}]$ follows from the fact that, for every node $x'\in V(T[a])$, every node $x$ on the path in $T$ from $a$ to  $x'$ is also a node of $T[a]$.  Therefore $(C_x:x\in V(T))$ is indeed a tree-decomposition of $J$.

>>>>

  Suppose, without loss of generality, that $v_0$ participates in $x_i$.  Then $a(v_0)=x$ is a $T$-ancestor of $x_i$ which is a $T$-ancestor of $x_r$.  Finally $a(v_r)=y$ is a $T$-ancestor of $x_r$.  Therefore, both $x$ and $y$ are contained in the path from the root of $T$ to $x_r$, so at least one of $x$ or $y$ is a $T$-ancestor of the other.  This completes the proof of \cref{i-ancestor}
\end{proof}

@@

\begin{proof}
  For the tree-decomposition $(C_x:x\in V(T))$ of $J$ we use the same tree $T$ used in the tree-decomposition $(B_x:x\in V(T))$ of $H$. For each node $x$ of $T$, we define $C_x$ as follows: $C_x$ contains $x$ as well as every $T$-ancestor $a$ of $x$ such that $J$ contains an edge $ax'$ where $x$ is a $T$-ancestor of $x'$ (including the possibility that $x=x'$).
  \cref{i-ancestor} ensures that, for every edge $ax'\in E(J)$, both $a$ and $x'$ are contained in $C_{x'}$.  The connectivity of $T[a]:=T[\{x\in V(T):a\in C_x\}]$ follows from the fact that, for every node $x'\in V(T[a])$, every node $x$ on the path in $T$ from $a$ to  $x'$ is also a node of $T[a]$.  Therefore $(C_x:x\in V(T))$ is indeed a tree-decomposition of $J$.
